Flowchart of Current Algorithm

### 2009-04-29 docs/flowchart/flowchart.tex
we now compute the time-centered psi in spherical with a time-centered gamma1bar rather than a base time gamma1bar

First use a predictor-corrector formulation for the pressure update 
in order to improve the overall accuracy.  Beginning with equation~(\ref{eq:w01}),
we can write
\begin{equation}
\frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} = 
 \Sbar - \frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) - \frac{1}{\gammabar p_0} w_0 \frac{\partial p_0}{\partial r} \enskip .
\end{equation}
We time-center the left hand side:
\begin{equation}
\frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} \approx
   \frac{2}{\gammabar^{\inp} (p_0^{\inp} + p_0^{\star})} \frac{p_0^{\star} - p_0^{\inp}}{\dt}\enskip.
\end{equation}
We can then solve for the provisional updated pressure, $p_0^{\star}$, giving:
\begin{equation}
p_0^{\star} = p_0^{\inp} \frac{\left(1 + \gammabar^{\inp} f\right)}{\left(1 - \gammabar^{\inp} f\right)}\enskip,
\end{equation}
with:
\begin{equation}
f = \frac{\dt}{2} \left [ \Sbar^{\inp} -  \frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0^{\inp} \right) - 
                                             \frac{1}{\gammabar^{\inp} p_0^{\inp}} w_0^{\inp} \left ( \frac{\partial p_0^\inp}{\partial r} \right ) \right ] \label{eq:frhs} \enskip ,
\end{equation}
where the $(\partial p_0^\inp / \partial r)$ is computed by
interpolating $p_0^\inp$ from cell-centers to edges and then
differencing.  Next, we compute a provisional updated $\gammabar$ using
$\gammabar^\star = {\bf Avg}[\Gamma_1(\rho^{\inp},p_0^\star,X_k^{\inp})]$,
where $\rho^\inp$ and $X_k^\inp$ are time-advanced versions of the $\rho$ and
$X_k$ used to compute $\gammabar^\inp$.\\

Now we begin the corrector step.  Using $p_0^\star$ and $\gammabar^\star$, 
we can compute a more accurate approximation to equation~(\ref{eq:frhs}),
\begin{equation}
f^\dagger = \frac{\dt}{2} \left [ \Sbar^{\inp} -  \frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0^{\inp} \right) - 
                                             \frac{1}{\gammabar^{\dagger} p_0^\dagger} w_0^{\inp} \left ( \frac{\partial p_0^\dagger}{\partial r} \right ) \right ] \enskip ,
\end{equation}
where $p_0^\dagger = (p_0^\inp + p_0^\star)/2$ and
$\gammabar^\dagger = (\gammabar^\inp + \gammabar^\star)/2$.
This allows us to complete the corrector for the pressure update:
\begin{equation}
p_0^{\outp} = p_0^{\inp} \frac{\left(1 + \gammabar^{\dagger} f^\dagger\right)}{\left(1 - \gammabar^{\dagger} f^\dagger\right)}\enskip .
\end{equation}
We note that since we do not time-center $\gammabar$, this is not
strictly second-order accurate.  However, as $\gammabar$ varies slowly
in time, we expect the effect to be small.  This is something that we 
defer until simulations indicate it is warranted.\\

Next, we compute $\psi^{\outp,n}$ and $\psi^{\outp,n+\myhalf}$.  Rewriting Equation 
(\ref{eq:w01}), we can define
\begin{eqnarray}
\psi \equiv \frac{D_0 p_0}{Dt} &=& \gammabar p_0 \left [ \overline{S} - 
       \frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) \right] \enskip .
\end{eqnarray}
We discretize this locally as:
\begin{equation}
\psi_j^{\outp,n} = 
\left(\gammabar^{\inp}p_0^{\inp}\right)_j
\left \{ \Sbar_j^{\inp} -  \frac{1}{r_j^2} \left [ (r^2 w_0^{\inp})_{j+\myhalf} -
          (r^2 w_0^{\inp})_{j-\myhalf} \right ] \right \} \enskip ,
\end{equation}
\begin{equation}
\psi_j^{\outp,n+\myhalf} = 
\left[\gammabar^{\inp} \frac{\left( p_0^{\inp} + p_0^{\outp} \right)}{2}\right]_j
\left \{ \Sbar_j^{\inp} -  \frac{1}{r_j^2} \left [ (r^2 w_0^{\inp})_{j+\myhalf} -
          (r^2 w_0^{\inp})_{j-\myhalf} \right ] \right \} \enskip .
\end{equation}
\end{description}

\item {\bf Advect Base Enthalpy}
is the process by which we update the base state enthalpy through $\dt$ in time.
The input arguments are different for plane-parallel and spherical.
\begin{description}
\item {\bf Advect Base Enthalpy Planar}$[(\rho h)_0^\inp,w_0^\inp,\psi^\inp] \rightarrow 
[(\rho h)_0^\outp]$

@@

\item {\bf Advect Base Enthalpy Spherical}$[(\rho h)_0^\inp,w_0^\inp,\psi^{\inp,n},
\psi^{\inp,n+\myhalf}] \rightarrow [(\rho h)_0^\outp]$

>>>>

First use a predictor-corrector formulation for the pressure update 
in order to improve the overall accuracy.  Beginning with equation~(\ref{eq:w01}),
we can write
\begin{equation}
\frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} = 
 \Sbar - \frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) - \frac{1}{\gammabar p_0} w_0 \frac{\partial p_0}{\partial r} \enskip .
\end{equation}
We time-center the left hand side:
\begin{equation}
\frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} \approx
   \frac{2}{\gammabar^{\inp} (p_0^{\inp} + p_0^{\star})} \frac{p_0^{\star} - p_0^{\inp}}{\dt}\enskip.
\end{equation}
We can then solve for the provisional updated pressure, $p_0^{\star}$, giving:
\begin{equation}
p_0^{\star} = p_0^{\inp} \frac{\left(1 + \gammabar^{\inp} f\right)}{\left(1 - \gammabar^{\inp} f\right)}\enskip,
\end{equation}
with:
\begin{equation}
f = \frac{\dt}{2} \left [ \Sbar^{\inp} -  \frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0^{\inp} \right) - 
                                             \frac{1}{\gammabar^{\inp} p_0^{\inp}} w_0^{\inp} \left ( \frac{\partial p_0^\inp}{\partial r} \right ) \right ] \label{eq:frhs} \enskip ,
\end{equation}
where the $(\partial p_0^\inp / \partial r)$ is computed by
interpolating $p_0^\inp$ from cell-centers to edges and then
differencing.  Next, we compute a provisional updated $\gammabar$ using the
provisional updated pressure,
$\gammabar^\star = {\bf Avg}[\Gamma_1(\rho^{\inp},p_0^\star,X_k^{\inp})]$,
where $\rho^\inp$ and $X_k^\inp$ are time-advanced versions of the $\rho$ and
$X_k$ which were used to compute $\gammabar^\inp$.\\

Now we begin the corrector step.  Using $p_0^\star$ and $\gammabar^\star$, 
we can compute a more accurate approximation to equation~(\ref{eq:frhs}),
\begin{equation}
f^\dagger = \frac{\dt}{2} \left [ \Sbar^{\inp} -  \frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0^{\inp} \right) - 
                                             \frac{1}{\gammabar^{\dagger} p_0^\dagger} w_0^{\inp} \left ( \frac{\partial p_0^\dagger}{\partial r} \right ) \right ] \enskip ,
\end{equation}
where $p_0^\dagger = (p_0^\inp + p_0^\star)/2$ and
$\gammabar^\dagger = (\gammabar^\inp + \gammabar^\star)/2$.
This allows us to complete the corrector for the pressure update:
\begin{equation}
p_0^{\outp} = p_0^{\inp} \frac{\left(1 + \gammabar^{\dagger} f^\dagger\right)}{\left(1 - \gammabar^{\dagger} f^\dagger\right)}\enskip .
\end{equation}
Next, we compute $\psi^{\outp,n}$ and $\psi^{\outp,n+\myhalf}$.  First, we compute an updated $\gammabar$ using the update pressure, $\gammabar^\star = {\bf Avg}[\Gamma_1(\rho^{\inp},p_0^{\outp},X_k^{\inp})]$.  Then, rewriting equation (\ref{eq:w01}), we can define
\begin{eqnarray}
\psi \equiv \frac{D_0 p_0}{Dt} &=& \gammabar p_0 \left [ \overline{S} - 
       \frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) \right] \enskip .
\end{eqnarray}
We discretize this locally as:
\begin{equation}
\psi_j^{\outp,n} = 
\left(\gammabar^\inp p_0^\inp\right)_j
\left \{ \Sbar_j^{\inp} -  \frac{1}{r_j^2} \left [ (r^2 w_0^{\inp})_{j+\myhalf} -
          (r^2 w_0^{\inp})_{j-\myhalf} \right ] \right \} \enskip ,
\end{equation}
\begin{equation}
\psi_j^{\outp,n+\myhalf} = 
\left(\frac{\gammabar^\inp+\gammabar^{\star}}{2}\right)_j
\left(\frac{p_0^\inp+p_0^\outp}{2}\right)_j
\left \{ \Sbar_j^{\inp} -  \frac{1}{r_j^2} \left [ (r^2 w_0^{\inp})_{j+\myhalf} -
          (r^2 w_0^{\inp})_{j-\myhalf} \right ] \right \} \enskip .
\end{equation}
\end{description}

\item {\bf Advect Base Enthalpy}
is the process by which we update the base state enthalpy through $\dt$ in time.
The input arguments are different for plane-parallel and spherical.
\begin{description}
\item {\bf Advect Base Enthalpy Planar}$[(\rho h)_0^\inp,w_0^\inp,\psi^\inp] \rightarrow 
[(\rho h)_0^\outp]$:

@@

\item {\bf Advect Base Enthalpy Spherical}$[(\rho h)_0^\inp,w_0^\inp,\psi^{\inp,n},
\psi^{\inp,n+\myhalf}] \rightarrow [(\rho h)_0^\outp]$:
